**Seasonal Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces**

### 2021-04-09 submission/manuscript.Rmd

	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x,big.mark=',', digits=1, nsmall=1, scientific=FALSE))
		}
	} else {
    	paste(x)      
	}
}
knitr::knit_hooks$set(inline=inline_hook)
```

@@

Obtained sequences were analysed on the computer cluster Isabella (University Computing Center, University of Zagreb) using mothur (version 1.43.0) [@Schloss2009] according to the MiSeq Standard Operating Procedure (MiSeq SOP; https://mothur.org/wiki/MiSeq_SOP) [@Kozich2013] and recommendations provided by the Riffomonas project to enhance data reproducibility (http://www.riffomonas.org/). For alignment and classification of sequences the SILVA SSU Ref NR 99 database (release 138; http://www.arb-silva.de) was used [@Quast2013; @Yilmaz2014]. Pipeline data processing and visualization was done using R (version 3.6.0) [@RCoreTeam2019] combined with  packages  vegan (version 2.5-6) [@Oksanen2019], tidyverse (version 1.3.0) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2020; @Allaire2019; @Xie2018; @Zhu2019; @Neuwirth2014; @Wilke2018]. The detailed analysis procedure including the R Markdown file are available in the GitHub repository (https://github.com/MicrobesRovinj/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021). Based on the ATCC MSA-1002 mock community included in the analysis an average sequencing error rate of `r error` \si{\percent} was determined, which is in line with previously reported values for next-generation sequencing data [@Kozich2013; @Schloss2016]. In addition, the negative controls processed together with the samples yielded on average only `r nc` sequences after sequence quality curation.

@@

# Calculating the number of sequences in millions
million_sequences <- filter(community, taxon=="Archaea" | taxon=="Bacteria") %>%
  select(total) %>%
  sum()/1e6

@@

# Calculating the relative abundance of Archaea and Bacteria
archaea_bacteria <- filter(community, taxon=="Archaea" | taxon=="Bacteria") %>%
  mutate_at(5:ncol(.), list(~. / sum(.) * 100)) %>%
  gather(key="Group", value="abundance", 6:(ncol(.))) %>%
  group_by(taxon) %>%
  summarise(mean=mean(abundance), sd=sd(abundance))
```

@@

# Generation of random rarefied community data
rarefied <- shared %>%
  select(-label, -Group, -numOtus) %>%
  rrarefy(., min(rowSums(.))) %>%
  as_tibble(.name_repair="unique") %>%
  add_column("Group"=shared$Group, .before=TRUE) %>%
  select_if(list(~ !is.numeric(.) || sum(.)!=0))

@@

```{r calculators}
# Copying the sample labels to the rows (input for library vegan)
row.names(rarefied) <- rarefied$Group

# Removing column containing sample labels
rarefied <- rarefied %>%
  select(-Group)

@@

Sequencing of the 16S rRNA V4 region yielded a total of `r million_sequences` million sequences after quality curation and exclusion of sequences without known relatives (no relative sequences) and eukaryotic, chloroplast and mitochondrial sequences (\autoref{supp-nseq_notus}). A total of `r samples_epiphytes` samples originating from epiphytic archaeal and bacterial communities associated with surfaces of the seagrass *C. nodosa* and the macroalga *C. cylindracea* were analysed. In addition, `r samples_seawater` samples (one of the samples was sequenced twice) originating from the ambient seawater were also processed for comparison. The number of reads per sample ranged between `r min_max$min` and `r min_max$max` sequences (\autoref{supp-nseq_notus}). Even when the highest sequencing effort was applied the rarefaction curves did not level off as commonly observed in high-throughput 16S rRNA amplicon sequencing approaches (\autoref{supp-rarefaction}). Following quality curation and exclusion of sequences as mentioned above reads were clustered into `r no_otus` different OTUs at a similarity level of 97 \si{\percent}. Read numbers were normalized to the minimum number of sequences (`r min_max$min`, \autoref{supp-nseq_notus}) through rarefaction resulting in `r no_otus_rarefied` different OTUs with `r min(otu_min_max)` to `r max(otu_min_max)` OTUs per sample (\autoref{supp-calculators}). To determine seasonal changes in richness and diversity the observed number of OTUs, Chao1, ACE, Exponential Shannon and Inverse Simpson [@Jost2006] were calculated after normalization through rarefaction. Generally, richness estimators and diversity indices showed similar trends. On average, higher values were found for *C. cylindracea* (mixed [Number of OTUs, `r S.obs_fcam$mean` ± `r S.obs_fcam$sd` OTUs] and monospecific [Number of OTUs, `r S.obs_fca$mean` ± `r S.obs_fca$sd` OTUs]) than for *C. nodosa* (Number of OTUs, `r S.obs_fcym$mean` ± `r S.obs_fcym$sd` OTUs) and lowest values were obtained for the microbial community of the ambient seawater (Number of OTUs, `r S.obs_f$mean` ± `r S.obs_f$sd` OTUs) (\autoref{supp-calculators}). Seasonal changes did not reveal such large dissimilarities. *C. nodosa* communities showed a slow increase towards the end of the study, while *C. cylindracea* (mixed and monospecific) communities were characterized by slightly higher values in spring and summer than in autumn and winter (\autoref{supp-calculators}).

```{r seasonal_shared}
# Generation of random rarefied community data
rarefied <- shared %>%
  select(-label, -Group, -numOtus) %>%
  rrarefy(., min(rowSums(.))) %>%
  as_tibble(.name_repair="unique") %>%
  add_column("Group"=shared$Group, .before=TRUE) %>%
  select_if(list(~ !is.numeric(.) || sum(.)!=0))

@@

# Joining metadata with OTU/sample data and summing sequences from each environment
rarefied_metadata <- inner_join(rarefied, metadata, by=c("Group"="ID")) %>%
  mutate(date=as.Date(date, "%d.%m.%Y")) %>%
  filter(date >= "2017-11-01") %>%
  select_if(list(~ !is.numeric(.) || sum(.)!=0)) %>%
  group_by(station) %>%
  summarise_at(vars(starts_with("Otu")), sum)

# Copying the sample labels to the rows (input for library vegan)
row.names(rarefied_metadata) <- rarefied_metadata$station

# Removing column containing sample labels
rarefied_metadata <- rarefied_metadata %>%
  select(-station)

@@

```{r core_otus}
# Joining metadata with OTU/sample data
metadata_rarefied <- inner_join(metadata, rarefied, by=c("ID"="Group")) %>%
  mutate(date=as.Date(date, "%d.%m.%Y"))

@@

```{r anosim}
# Generation of random rarefied community data and preserving sample names as row names
rarefied <- shared %>%
  select(-label, -Group, -numOtus) %>%
  rrarefy(., min(rowSums(.))) %>%
  as_tibble(.name_repair="unique") %>%
  select_if(list(~!is.numeric(.) || sum(.)!=0))
rownames(rarefied) <- shared$Group
rarefied <- rarefied %>%
  add_column("Group"=shared$Group, .before=TRUE)

@@

Sequences classified as *Bacteroidota* comprised, on average, `r bactero_all_whole$mean` ± `r bactero_all_whole$sd` \si{\percent} of all sequences (\autoref{bactero}). Similarly to *Cyanobacteria*, large differences in the taxonomic composition between ambient seawater and surface associated communities were found (\autoref{bactero}). The ambient seawater community was characterized by the NS4 and NS5 marine groups, uncultured *Cryomorphaceae*, uncultured *Flavobacteriaceae*, NS11-12 marine group, *Balneola*, uncultured *Balneolaceae* and *Formosa*. In contrast, in surface associated communities *Lewinella*, *Portibacter*, *Rubidimonas*, sequences without known relatives within the *Saprospiraceae* (no relative *Saprospiraceae*), uncultured *Saprospiraceae*, (sequences without known relatives within the *Flavobacteriaceae* (no relative *Flavobacteriaceae*)and uncultured *Rhodothermaceae* were found. Some groups showed minor seasonal changes such as no relative *Flavobacteriaceae* whose sequences were more abundant from November 2017 until June 2018. In contrast, uncultured *Rhodothermaceae* showed higher proportions from June 2018 until the end of the study period. Surface associated *Bacteroidota* communities were very diverse as observed in the high proportion of taxa clustering as other *Bacteroidota* (\autoref{bactero}).

@@

## Acknowledgments
This work was founded by the Croatian Science Foundation through the MICRO-SEAGRASS project (project number IP-2016-06-7118). ZZ and GJH were supported by the Austrian Science Fund (FWF) project ARTEMIS (project number P28781-B21). We would like to thank Margareta Buterer for technical support, Paolo Paliaga for help during sampling and the University Computing Center of the University of Zagreb for access to the computer cluster Isabella.

@@

## Figures
```{r out.width="70%", fig.align="center", fig.cap="Proportion of shared bacterial and archaeal OTUs (Jaccard's similarity coefficient) and shared bacterial and archaeal communities (Bray-Curtis similarity coefficient) between assemblages associated with the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and communities in the ambient seawater.\\label{matrix}", fig.pos="H"}
include_graphics("../results/figures/matrix.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Proportion of shared bacterial and archaeal communities (Bray-Curtis similarity coefficient) and shared bacterial and archaeal OTUs (Jaccard's similarity coefficient) between consecutive sampling dates and from the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater.\\label{shared}", fig.pos="H"}
include_graphics("../results/figures/seasonal_shared.jpg")
```

```{r out.width="55%", fig.align="center", fig.cap="Principal Coordinates Analysis (PCoA) of Bray-Curtis distances based on OTU abundances of bacterial and archaeal communities from the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. Samples from the same environment or same season are labeled in different colors. The proportion of explained variation by each axis is shown on the corresponding axis in parentheses.\\label{pcoa}", fig.pos="H"}
include_graphics("../results/figures/pcoa_figure.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 1 \\si{\\percent}) bacterial and archaeal sequences on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{community}", fig.pos="H"}
include_graphics("../results/figures/community_bar_plot.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 1 \\si{\\percent}) cyanobacterial sequences on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. The proportion of cyanobacterial sequences in the total bacterial and archaeal community is given above the corresponding bar. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{cyano}", fig.pos="H"}
include_graphics("../results/figures/cyanobacteria_bar_plot.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 2 \\si{\\percent}) sequences within the \\textit{Bacteroidota} on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. The proportion of sequences classified as \\textit{Bacteroidota} in the total bacterial and archaeal community is given above the corresponding bar. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{bactero}", fig.pos="H"}
include_graphics("../results/figures/bacteroidota_bar_plot.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 2 \\si{\\percent}) alphaproteobacterial sequences on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. The proportion of alphaproteobacterial sequences in the total bacterial and archaeal community is given above the corresponding bar. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{alpha}", fig.pos="H"}
include_graphics("../results/figures/alphaproteobacteria_bar_plot.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 1 \\si{\\percent}) gammaproteobacterial sequences on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. The proportion of gammaproteobacterial sequences in the total bacterial and archaeal community is given above the corresponding bar. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{gamma}", fig.pos="H"}
include_graphics("../results/figures/gammaproteobacteria_bar_plot.jpg")

@@

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 1 \\si{\\percent}) sequences within the \\textit{Desulfobacterota} on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. The proportion of sequences classified as \\textit{Desulfobacterota} in the total bacterial and archaeal community is given above the corresponding bar. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{desulfo}", fig.pos="H"}
include_graphics("../results/figures/desulfobacterota_bar_plot.jpg")
```

>>>>

	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x, big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x, big.mark=',', digits=1, nsmall=1, scientific=FALSE))
		}
	} else {
    	paste(x)      
	}
}
knitr::knit_hooks$set(inline=inline_hook)
```

@@

Obtained sequences were analysed on the computer cluster Isabella (University Computing Center, University of Zagreb) using mothur (version 1.43.0) [@Schloss2009] according to the MiSeq Standard Operating Procedure (MiSeq SOP; https://mothur.org/wiki/MiSeq_SOP) [@Kozich2013] and recommendations provided by the Riffomonas project to enhance data reproducibility (http://www.riffomonas.org/). For alignment and classification of sequences the SILVA SSU Ref NR 99 database (release 138; http://www.arb-silva.de) was used [@Quast2013; @Yilmaz2014]. Pipeline data processing and visualization was done using R (version 3.6.0) [@RCoreTeam2019] combined with  packages  vegan (version 2.5-6) [@Oksanen2019], tidyverse (version 1.3.0) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2019b; @Allaire2019; @Xie2018; @Zhu2019; @Neuwirth2014; @Wilke2018]. The detailed analysis procedure including the R Markdown file are available in the GitHub repository (https://github.com/MicrobesRovinj/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021). Based on the ATCC MSA-1002 mock community included in the analysis an average sequencing error rate of `r error` \si{\percent} was determined, which is in line with previously reported values for next-generation sequencing data [@Kozich2013; @Schloss2016]. In addition, the negative controls processed together with the samples yielded on average only `r nc` sequences after sequence quality curation.

@@

# Calculating the number of sequences in millions
million_sequences <- filter(community, taxon=="Archaea" | taxon=="Bacteria") %>%
  select(6:ncol(.)) %>%
  sum()/1e6

@@

# Calculating the relative abundance of Archaea and Bacteria
archaea_bacteria <- filter(community, taxon=="Archaea" | taxon=="Bacteria") %>%
  mutate_at(5:ncol(.), list(~. / sum(.) * 100)) %>%
  gather(key="Group", value="abundance", 6:ncol(.)) %>%
  group_by(taxon) %>%
  summarise(mean=mean(abundance), sd=sd(abundance))
```

@@

# Loading rarefied community data created during the generation of the richness and diversity calculators plot
load(file="results/numerical/rarefied.Rdata")

@@

```{r calculators}
# Loading rarefied community data created during the generation of the richness and diversity calculators plot
load(file="results/numerical/rarefied.Rdata")

# Copying the sample labels to the rows (input for library vegan)
rarefied <- rarefied %>%
  column_to_rownames("Group")

@@

Sequencing of the 16S rRNA V4 region yielded a total of `r million_sequences` million sequences after quality curation and exclusion of sequences without known relatives (no relative sequences) and eukaryotic, chloroplast and mitochondrial sequences (\autoref{supp-nseq_notus}). A total of `r samples_epiphytes` samples originating from epiphytic archaeal and bacterial communities associated with surfaces of the seagrass *C. nodosa* and the macroalga *C. cylindracea* were analysed. In addition, `r samples_seawater` samples (one of the samples was sequenced twice) originating from the ambient seawater were also processed for comparison. The number of reads per sample ranged between `r min_max$min` and `r min_max$max` sequences (\autoref{supp-nseq_notus}). Even when the highest sequencing effort was applied the rarefaction curves did not level off as commonly observed in high-throughput 16S rRNA amplicon sequencing approaches (\autoref{supp-rarefaction}). Following quality curation and exclusion of sequences as mentioned above reads were clustered into `r no_otus` different OTUs at a similarity level of 97 \si{\percent}. Read numbers were normalized to the minimum number of sequences (`r min_max$min`, \autoref{supp-nseq_notus}) through rarefaction resulting in `r no_otus_rarefied` different OTUs with `r min(otu_min_max)` to `r max(otu_min_max)` OTUs per sample (\autoref{supp-calculators}). To determine seasonal changes in richness and diversity the observed number of OTUs, Chao1, ACE, Exponential Shannon and Inverse Simpson [@Jost2006] were calculated after normalization through rarefaction. Generally, richness estimators and diversity indices showed similar trends. On average, higher values were found for *C. cylindracea* (mixed [Number of OTUs, `r S.obs_fcam$mean` ± `r S.obs_fcam$sd` OTUs] and monospecific [Number of OTUs, `r S.obs_fca$mean` ± `r S.obs_fca$sd` OTUs]) than for *C. nodosa* (Number of OTUs, `r S.obs_fcym$mean` ± `r S.obs_fcym$sd` OTUs) and lowest values were obtained for the microbial community of the ambient seawater (Number of OTUs, `r format(S.obs_f$mean, digits=1, nsmall=1)` ± `r S.obs_f$sd` OTUs) (\autoref{supp-calculators}). Seasonal changes did not reveal such large dissimilarities. *C. nodosa* communities showed a slow increase towards the end of the study, while *C. cylindracea* (mixed and monospecific) communities were characterized by slightly higher values in spring and summer than in autumn and winter (\autoref{supp-calculators}).

```{r seasonal_shared}
# Loading rarefied community data created during the generation of the richness and diversity calculators plot
load(file="results/numerical/rarefied.Rdata")

@@

# Joining metadata with OTU/sample data and summing sequences from each environment
rarefied_metadata <- inner_join(rarefied, metadata, by=c("Group"="ID")) %>%
  mutate(date=as.Date(date, "%d.%m.%Y")) %>%
  filter(date >= "2017-11-01") %>%
  select(!where(is.numeric) | where(~is.numeric(.x) && sum(.x)!=0)) %>%
  group_by(station) %>%
  summarise(across(starts_with("Otu"), sum), .groups="drop")

# Copying the sample labels to the rows (input for library vegan)
rarefied_metadata <- rarefied_metadata %>%
  column_to_rownames("station")

@@

```{r core_otus}
# Loading rarefied community data created during the generation of the richness and diversity calculators plot
load(file="results/numerical/rarefied.Rdata")

# Joining metadata with OTU/sample data
metadata_rarefied <- read_tsv("data/raw/metadata.csv") %>%
  inner_join(., rarefied, by=c("ID"="Group")) %>%
  mutate(date=as.Date(date, "%d.%m.%Y"))

@@

```{r anosim}
# Loading rarefied community data created during the generation of the richness and diversity calculators plot
load(file="results/numerical/rarefied.Rdata")

@@

Sequences classified as *Bacteroidota* comprised, on average, `r bactero_all_whole$mean` ± `r bactero_all_whole$sd` \si{\percent} of all sequences (\autoref{bactero}). Similarly to *Cyanobacteria*, large differences in the taxonomic composition between ambient seawater and surface associated communities were found (\autoref{bactero}). The ambient seawater community was characterized by the NS4 and NS5 marine groups, uncultured *Cryomorphaceae*, uncultured *Flavobacteriaceae*, NS11-12 marine group, *Balneola*, uncultured *Balneolaceae* and *Formosa*. In contrast, in surface associated communities *Lewinella*, *Portibacter*, *Rubidimonas*, sequences without known relatives within the *Saprospiraceae* (no relative *Saprospiraceae*), uncultured *Saprospiraceae*, (sequences without known relatives within the *Flavobacteriaceae* (no relative *Flavobacteriaceae*) and uncultured *Rhodothermaceae* were found. Some groups showed minor seasonal changes such as no relative *Flavobacteriaceae* whose sequences were more abundant from November 2017 until June 2018. In contrast, uncultured *Rhodothermaceae* showed higher proportions from June 2018 until the end of the study period. Surface associated *Bacteroidota* communities were very diverse as observed in the high proportion of taxa clustering as other *Bacteroidota* (\autoref{bactero}).

@@

## Acknowledgments
This work was funded by the Croatian Science Foundation through the MICRO-SEAGRASS project (project number IP-2016-06-7118). ZZ and GJH were supported by the Austrian Science Fund (FWF) project ARTEMIS (project number P28781-B21). We would like to thank Margareta Buterer for technical support, Paolo Paliaga for help during sampling and the University Computing Center of the University of Zagreb for access to the computer cluster Isabella.

@@

## Figures
```{r out.width="70%", fig.align="center", fig.cap="Proportion of shared bacterial and archaeal OTUs (Jaccard's similarity coefficient) and shared bacterial and archaeal communities (Bray-Curtis similarity coefficient) between assemblages associated with the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and communities in the ambient seawater.\\label{matrix}", fig.pos="H"}
include_graphics(normalizePath("results/figures/matrix.jpg"))
```

```{r out.width="85%", fig.align="center", fig.cap="Proportion of shared bacterial and archaeal communities (Bray-Curtis similarity coefficient) and shared bacterial and archaeal OTUs (Jaccard's similarity coefficient) between consecutive sampling dates and from the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater.\\label{shared}", fig.pos="H"}
include_graphics(normalizePath("results/figures/seasonal_shared.jpg"))
```

```{r out.width="55%", fig.align="center", fig.cap="Principal Coordinates Analysis (PCoA) of Bray-Curtis distances based on OTU abundances of bacterial and archaeal communities from the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. Samples from the same environment or same season are labeled in different colors. The proportion of explained variation by each axis is shown on the corresponding axis in parentheses.\\label{pcoa}", fig.pos="H"}
include_graphics(normalizePath("results/figures/pcoa_figure.jpg"))
```

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 1 \\si{\\percent}) bacterial and archaeal sequences on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{community}", fig.pos="H"}
include_graphics(normalizePath("results/figures/community_bar_plot.jpg"))
```

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 1 \\si{\\percent}) cyanobacterial sequences on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. The proportion of cyanobacterial sequences in the total bacterial and archaeal community is given above the corresponding bar. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{cyano}", fig.pos="H"}
include_graphics(normalizePath("results/figures/cyanobacteria_bar_plot.jpg"))
```

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 2 \\si{\\percent}) sequences within the \\textit{Bacteroidota} on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. The proportion of sequences classified as \\textit{Bacteroidota} in the total bacterial and archaeal community is given above the corresponding bar. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{bactero}", fig.pos="H"}
include_graphics(normalizePath("results/figures/bacteroidota_bar_plot.jpg"))
```

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 2 \\si{\\percent}) alphaproteobacterial sequences on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. The proportion of alphaproteobacterial sequences in the total bacterial and archaeal community is given above the corresponding bar. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{alpha}", fig.pos="H"}
include_graphics(normalizePath("results/figures/alphaproteobacteria_bar_plot.jpg"))
```

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 1 \\si{\\percent}) gammaproteobacterial sequences on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. The proportion of gammaproteobacterial sequences in the total bacterial and archaeal community is given above the corresponding bar. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{gamma}", fig.pos="H"}
include_graphics(normalizePath("results/figures/gammaproteobacteria_bar_plot.jpg"))

@@

```{r out.width="85%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant ($\\geq$ 1 \\si{\\percent}) sequences within the \\textit{Desulfobacterota} on the surfaces of the macrophytes \\textit{C. nodosa} (mixed settlement) and \\textit{C. cylindracea} (mixed and monospecific settlement) and in the ambient seawater. The proportion of sequences classified as \\textit{Desulfobacterota} in the total bacterial and archaeal community is given above the corresponding bar. NR -- No Relative (sequences without known relatives within the corresponding group)\\label{desulfo}", fig.pos="H"}
include_graphics(normalizePath("results/figures/desulfobacterota_bar_plot.jpg"))
```
